---
title: 'Homework #6'
author: 'Kobe Pranivong; illuminobe'
date: '4/24/2020'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library("dplyr")
library("tidyr")
library("tidyverse")
library("ggplot2")
library("readxl")
library("ggrepel")
library("RColorBrewer")
```

## Top dogs

In this homework, you will try to reproduce the fantastic infographic for [top dogs](https://informationisbeautiful.net/visualizations/best-in-show-whats-the-top-data-dog/), originally produced by David McCandless. The raw data can be found [here](https://docs.google.com/spreadsheets/d/1l_HfF5EaN-QgnLc2UYdCc7L2CVrk0p3VdGB1godOyhk/edit#gid=10). You can download this file by File -- Download As -- Microsoft Excel (.xlsx).

**Submission instructions**: Create a folder named `ds202_hw6`, and name the RMarkDown file including your solutions `hw6.Rmd` under this folder. For the submission, create a GitHub repository named `ds202_hw6` under your GitHub account, and push both `hw6.Rmd` and the knitted `hw6.html` before the deadline. I will assume you use the same GitHub username as for your HW5 submission. The latest version of your homework appearing on GitHub before the deadline is graded. *It is crucial to follow the exact folder structure and file names*, so that your homework can be reproduced and graded by an automated script. This homework is **due on April 22** before class.

1. Import the data and clean appropriately. To read in the data, you can use `readxl::read_xlsx('fileNameHere', sheet='sheetNameHere')`. Required data are in the sheets `Best in show` and `Best in show full sheet`. Take extra care on the column names and the first few rows of the data frame after read in.
```{r}
df <- readxl::read_xlsx("KIB.xlsx", sheet = "Best in show full sheet")
df1 <- readxl::read_xlsx("KIB.xlsx", sheet = "Best in show")
df <- df[, colSums(is.na(df))<nrow(df)]
df <- df %>% 
  select(1, 2, 3, 5, 9, 27)
df <- df[-c(1, 2, 3), ]
colnames(df) <- c("Breed", "Type", "Score", "Popularity", "Intelligence_Raw", "Size")
df$Score <- as.numeric(df$Score)
df$Popularity <- as.numeric(df$Popularity)
df$Intelligence_Raw <- as.numeric(df$Intelligence_Raw)
df$Type <- as.factor(df$Type)
df$Size <- as.factor(df$Size)
df$Size <- fct_rev(df$Size)
df <- df %>% 
  mutate(Intelligence = ifelse(Intelligence_Raw >= 0.5, "Clever", "Dumb"))
df$Intelligence <- as.factor(df$Intelligence)
df$Intelligence <- fct_rev(df$Intelligence)
df <- df %>% drop_na()
df %>% head
```
2. Create a graphics similar to the  [top dogs](https://informationisbeautiful.net/visualizations/best-in-show-whats-the-top-data-dog/) figure. Your figure needs to display the following information with appropriate plotting elements:

- breed of dog
- type of dog (work, toy, etc.)
- size of dog
- data score 
- popularity
- intelligence of the dog
- appropriate legends & explanation

Hints and Notes:

- The breed of dog can be displayed without the silhouttes (text only is fine)
- Avoid (too much) overlaps!
- Choose a good color scheme.

```{r}
minimum_score <- min(as.vector(df$Score), na.rm = TRUE)
maximum_score <- max(as.vector(df$Score), na.rm = TRUE)
score_range <- maximum_score - minimum_score
score_middle <- score_range / 2 + minimum_score
minimum_popularity <- -max(as.vector(df$Popularity), na.rm = TRUE)
maximum_popularity <- -min(as.vector(df$Popularity), na.rm = TRUE)
popularity_range <- maximum_popularity - minimum_popularity
popularity_middle <- popularity_range / 2 + minimum_popularity
plot <- ggplot(df, aes(x = Score, y = -Popularity, label = Breed)) + 
  geom_point(alpha = 0.8, aes(shape = Intelligence, color = Type, size = Size)) +
  xlab("Our Data Score") + ylab("Popularity") + ggtitle("Best in Show: The Ultimate Data Dog") +
  coord_cartesian(xlim = c(minimum_score - score_range * 0.01, maximum_score + score_range * 0.01),
                  ylim = c(minimum_popularity - popularity_range * 0.03, maximum_popularity + popularity_range * 0.03)) +
  geom_vline(xintercept = score_middle, size = 0.5) +
  geom_hline(yintercept = popularity_middle, size = 0.5) +
  theme(axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        plot.title = element_text(lineheight = .8, face = "bold")) +
  geom_text_repel(aes(color = Type), size = 1) +
  scale_size_discrete(breaks = levels(df$Size)) +
  annotate("text", x = minimum_score - score_range * 0.05, 
           y = minimum_popularity - popularity_range * 0.05, label = "The Rightly Ignored", hjust = 0) +
  annotate("text", x = maximum_score + score_range * 0.05, 
           y = maximum_popularity + popularity_range * 0.05, label = "Hot Dogs!", hjust = 1) +
  annotate("text", x = minimum_score - score_range * 0.05, 
           y = maximum_popularity + popularity_range * 0.05, label = "Inexplicably Overrated", hjust = 0) +
  annotate("text", x = maximum_score + score_range * 0.05, 
           y = minimum_popularity - popularity_range * 0.05, label = "Overlooked Treasures", hjust = 1) +
  guides(shape = guide_legend(order = 1),
         size = guide_legend(order = 2),
         color = guide_legend(order = 3)) +
  scale_color_brewer(palette = "Dark2")
plot
```

- Your submission is supposed to be fully reproducible, i.e. the TA and I will 'knit' your submission in RStudio. 